A study of the effects of within functional group diversity on the response

### 2021-04-16 various_stuff/dev_vignettes/within-function-group-diversity.Rmd
various

```{r}
default_log10a_series <- c(log10(default_parameter_values["a_O"]),
                           log10(default_parameter_values["a_O"]))
```

@@

simulation_result <- run_simulation(dynamic_model =
                                      bushplus_dynamic_model_strains,
                                    parameter_values = one_strain_params,
                                    initial_state = one_strain_initial_state)

@@

multi_strain_params <- construct_parameter_set(CB_strain_params,
                                    PB_strain_params,
                                    SB_strain_params,
                                    all_other_parms)

multi_strain_initial_state <- c(
  CB_1 = 5e1,
  CB_2 = 0,
  CB_3 = 0,
  PB_1 = 1e7,
  PB_2 = 1e6,
  PB_3 = 1e5,
  SB_1 = 1e7,
  SB_2 = 1e6,
  SB_3 = 1e5,
  SO = 300,
  SR = 300,
  O = 1e1,
  P = 1e1)

simulation_result <- run_simulation(dynamic_model = bushplus_dynamic_model_strains,
               parameter_values = multi_strain_params,
               initial_state = multi_strain_initial_state)
plot_dynamics_strains(simulation_result)

>>>>

```{r}
default_parameter_values <- return_default_parameter_values()
default_log10a_series <- c(log10(default_parameter_values["a_O"]),
                           log10(default_parameter_values["a_O"]))
```

@@

simulation_result <- run_simulation(dynamic_model = bushplus_dynamic_model_strains,
                                    parameter_values = one_strain_params,
                                    initial_state = one_strain_initial_state,
                                    event_definition = default_event_definition_strains)

@@

multi_strain_params <- construct_parameter_set(CB_strain_params,
                                    PB_strain_params,
                                    SB_strain_params,
                                    all_other_params)

multi_strain_initial_state <- c(
  CB_1 = 5e3,
  CB_2 = 1e3,
  CB_3 = 0,
  PB_1 = 1e7,
  PB_2 = 1e6,
  PB_3 = 1e5,
  SB_1 = 1e7,
  SB_2 = 1e6,
  SB_3 = 1e5,
  SO = 300,
  SR = 300,
  O = 1e1,
  P = 1e1)

simulation_result <- run_simulation(dynamic_model = bushplus_dynamic_model_strains,
               parameter_values = multi_strain_params,
               initial_state = multi_strain_initial_state,
               event_definition = default_event_definition_strains)
